---
title: "Task 1. SWQ Standards"
author: "Mike Allen"
date: "2/4/2022"
output: html_document
---
# Task 1: Surface Water Quality Standards (SWQS)
a. Analyze logger data to determine if select monitoring reaches are impaired for sensitive aquatic life (e.g., macroinvertebrates, trout) in freshwater streams. 
- Analyze daily/monthly data at each monitoring location against state SWQS criteria. Which sites are meeting/not meeting SWQS (do temperatures and dissolved oxygen meet criteria required to support aquatic life and trout?)?
b. How often do sites exceed SWQS for temperature (how many days per year)?
c. How often do sites exceed SWQS for dissolved oxygen (how many days per year)?


# Product 1:
• Data visualization (figures, maps, plots) of seasonal, monthly, and diel fluctuations in flow, physiochemical conditions to address the items in Task 1 with respect to state water quality criteria.

• Meetings as needed to refine objectives and desired outputs.

• Summary statistics and statistical analysis of same along with associated interpretative text.

# Load libraries etc.
```{r}
library(dplyr)
library(knitr)
library(kableExtra)
library(lubridate)
library(wesanderson)
library(ggplot2)
library(forcats)

# read in compiled logger data (including flagged data)
p <- readRDS("output/compiled_hydro_hobo.rds") %>%
  mutate(order = as.numeric(substr(site, 5, 6)),
         site = fct_reorder(site, order)) %>%
  filter(order < 80)

# full list of tmax sites and days
tmax_all <- 

tmax <- p %>%
  filter(FLAG_Temp == 0) %>%
  mutate(day = yday(datetime)) %>%
  group_by(site, year, day) %>%
  summarise(max_temp = max(temp),
            .groups = "drop") %>%
  group_by(site, year) %>%
  mutate(roll_temp = zoo::rollmean(max_temp, 7, fill = NA)) %>%
  droplevels() %>%
  ungroup() %>%
  # remove obvious outliers at start of time series
  filter(as.logical(1-(site == "TNC_25" & year == 2018 & day == 122))) %>%
  filter(as.logical(1-(site == "TNC_23" & year == 2018 & day == 122))) %>%
  filter(as.logical(1-(site == "TNC_23" & year == 2021 & day == 118))) %>%
  right_join(expand.grid(site = unique(p$site), year = 2016:2021, day = 82:339)) %>%
  arrange(site, year, day)



```

# Temperature SWQS
b. How often do sites exceed SWQS for temperature (how many days per year)?

From the QAPP:
	1. FW2-TP - Temperature	Shall not exceed a daily maximum of 22 degrees Celsius or rolling seven-day average of the daily maximum of 19 degrees Celsius, unless due to natural conditions
	  - How many days exceed 22 C
	  - How many days 7-d rolling average of daily max exceed 19 C
	
	2. FW2-TM - Shall not exceed a daily maximum of 25 degrees Celsius or rolling seven-day average of the daily maximum of 23 degrees Celsius, unless due to natural conditions	
    - How many days exceed 25 C
    - How many days 7-d rolling average of daily max exceed 23 C

	3. FW2-NT - Shall not exceed a daily maximum of 31 degrees Celsius or rolling seven-day average of the daily maximum of 28 degrees Celsius, unless due to natural conditions	
	
# Temperature SWQS 1: plot daily max temp for each site/year vs. thresholds
To do: 
1. add in NAs to days with missing values so lines don't interpolate

```{r}
# plot daily max vs. thresholds
tmax %>%
  ggplot() +
  geom_hline(yintercept = 22, color = "gray", lty = 3, size = .75) +
  geom_hline(yintercept = 25, color = "gray", lty = 2, size = .75) +
  geom_hline(yintercept = 31, color = "gray", lty = 1, size = .75) + 
  geom_line(aes(x = day, y = max_temp, 
                 color = as.factor(year)),
             alpha = 0.75) +
  facet_wrap(~site) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(y = "Daily maximum temperature (C)", x = "Day of year",
       color = "Year")

ggsave("output/Task1/tmax_by_day_year_site.png", 
       height = 7, width = 9, dpi = 400)
```
# Temperature SWQS 1: plot rolling-average daily max temp for each site/year vs. thresholds
To do: 

```{r}
# plot rolling average daily max vs. thresholds
tmax %>%
  ggplot() +
  geom_hline(yintercept = 19, color = "gray", lty = 3, size = .75) +
  geom_hline(yintercept = 23, color = "gray", lty = 2, size = .75) +
  geom_hline(yintercept = 28, color = "gray", lty = 1, size = .75) +
  geom_line(aes(x = day, y = roll_temp, 
                 color = as.factor(year)),
             alpha = 0.75) +
  facet_wrap(~site) +
  scale_color_brewer(palette = "Dark2") +
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(y = "Daily maximum temperature: \n7-day rolling average (C)", x = "Day of year",
       color = "Year")

ggsave("output/Task1/tmax_by_day_year_site_rolling.png", 
       height = 7, width = 9, dpi = 400)
```
# create table of number of temp measurement days per year per site
```{r}
# create table with Kable
tmax_table <- tmax %>%
  droplevels() %>%
  filter(is.na(max_temp) != T)
day_table <- table(tmax_table$site, tmax_table$year) %>%
  kbl(caption = "Number of days of temperature data by site and year.") %>%
  kable_classic(full_width = F, html_font = "Cambria")

# save the table to HTML file
save_kable(day_table, "output/Task1/tmax_n_table.html")

# remove tmax_table object
rm(tmax_table)
```

# Calculate number of days exceeding temperature thresholds
```{r}
temp_count <- tmax %>%
  filter(is.na(max_temp)==F) %>%
  mutate(max_22 = ifelse(max_temp > 22, 1, 0),
         max_25 = ifelse(max_temp > 25, 1, 0),
         max_31 = ifelse(max_temp > 31, 1, 0),
         roll_19 = ifelse(roll_temp > 19, 1, 0),
         roll_23 = ifelse(roll_temp > 23, 1, 0),
         roll_28 = ifelse(roll_temp > 28, 1, 0)) %>%
  group_by(site, year) %>%
  summarise(max_22 = sum(max_22),
            max_25 = sum(max_25),
            max_31 = sum(max_31),
            roll_19 = sum(roll_19, na.rm = T),
            roll_23 = sum(roll_23, na.rm = T),
            roll_28 = sum(roll_28, na.rm = T)) %>%
  tidyr::pivot_longer(cols = 3:8)

ggplot(temp_count) +
  geom_line(aes(x = year, y = value, color = name)) +
  geom_point(aes(x = year, y = value, color = name), size = 2) +
  facet_wrap(~site) +
  scale_color_brewer(palette = "Dark2")


```

c. How often do sites exceed SWQS for dissolved oxygen (how many days per year)?
```{r}

```

