---
title: "Task 3. project impacts"
author: "Mike Allen"
date: "2/28/2022"
output:
  html_document: default
  pdf_document: default
---
# How to run this code
Run the first section ("chunk") of this Rmd document (section 3.0). That will load all libraries, functions, and data. After that, you can scroll down to the plot or table you wish to make or the model you wish to run and run just that section. Plots, tables and models are labeled with letters (A-Z) and correspond to those in the "Task 3" sub-folder in the "output" folder. See the README file in that sub-folder for figure captions and information.

The following text is a general description of Task 3.

# Task 3: Project Specific Analyses
a. What are water quality conditions upstream/downstream/within project area(s) pre and post dam removal (assessing turbidity, conductivity, dissolved oxygen and temperature)?

b. What are baseline water quality conditions 
upstream/downstream/within floodplain reforestation corridor(s) before and after tree plantings (assessing temperature, dissolved oxygen)?

c. What are baseline water quality conditions downstream Hyper Humus (assessing temperature, dissolved oxygen)?

Task and Product 3 Due: April 10, 2022

Products:
• Evaluate project specific questions via statistical analysis and data visualization (figures, maps, plots).
• Meetings as needed to refine objectives and desired outputs.
• Assess spatial and temporal changes in water quality metrics with respect to dam removal (before/after, upstream/downstream), restoration projects, and other sites of interest (Hyper Humus). Provide associated interpretative text.

# 3.0. Load libraries, format data, etc.
```{r}
library(dplyr)
library(knitr)
library(tidyr)
library(kableExtra)
library(wesanderson)
library(lubridate)
library(ggplot2)
library(forcats)
# library(lme4)
library(here)
'%notin%' <- Negate('%in%')
task_path <- "output/Task3_project_impacts/"

# read in compiled logger data (including flagged data)
p <- readRDS("output/compiled_logger_data.rds") %>%
  mutate(order = as.numeric(substr(site, 5, 6)),
         site = fct_reorder(site, order))

# format final compiled temperature data
tdata <- p %>%
  filter(FLAG_Temp == 0) %>%
  mutate(day = yday(datetime),
         month = month(datetime),
         hour = hour(datetime),
         minute = minute(datetime),
         dtime = hour + minute/60) %>%
  # remove obvious outliers at start of time series
  filter(as.logical(1-(site == "TNC_25" & 
                         year == 2018 & 
                         day == 122))) %>%
  filter(as.logical(1-(site == "TNC_23" & 
                         year == 2018 & 
                         day == 122))) %>%
  filter(as.logical(1-(site == "TNC_23" & 
                         year == 2021 & 
                         day == 118))) %>%
  arrange(site, year, day) %>%
  # peak movement ~ 15 April - 15 May in Raritan per Anthony V.
  mutate(season = case_when(day %in% 105:135 ~ "migrate", #4/15-5/15
                            day %in% 136:151 ~ "spawn", #5/16-5/31
                            day %in% 152:181 ~ "larvae", #6/1-6/30
                            day %in% 182:258 ~ "juvenile", #7/1-9/15
                            day %in% 259:334 ~ "fall_mig"), #9/15-11
         yearf = as.factor(year),
         dayf = as.factor(day),
         hourf = as.factor(hour),
         season = as.factor(season))

# Columbia Dam - Temperature
    # upstream: TNC_23, downstream: TNC_25 (& 24), in: 80 & 81
col <- tdata %>%
  filter(site %in% c("TNC_23", "TNC_25", 
                     "TNC_24", "TNC_81", "TNC_80")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_temp = mean(temp),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_temp = mean(mean_temp),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_temp") %>%
  mutate(d25.23 = TNC_25-TNC_23,
         d25.80 = TNC_25-TNC_80,
         d25.81 = TNC_25-TNC_81,
         stage = as.factor(case_when(yearf %in% 2016:2017 ~ 1,
                           yearf == 2018 & as.numeric(as.character(monthf))<7~1,
                           yearf == 2018 & as.numeric(as.character(monthf))>=7 |
                             yearf == 2019 & as.numeric(as.character(monthf))<5~2,
                           yearf == 2019 & as.numeric(as.character(monthf))>=5~3,
                           yearf %in% 2020:2051 ~ 3))
         )

# Tree planting area - Temperature
    # upstream: TNC_4, within: TNC_5, downstream: TNC_8
tree <- tdata %>%
  filter(site %in% c("TNC_4", "TNC_5", "TNC_8")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_temp = mean(temp),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_temp = mean(mean_temp),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_temp") %>%
  mutate(d8.4 = TNC_8-TNC_4,
         d5.4 = TNC_5-TNC_4,
         d4.8 = TNC_4-TNC_8,
         d4.5 = TNC_4-TNC_5,
         stage = as.factor(case_when(yearf %in% 2016:2018 ~ 1,
                           yearf %in% 2019:2051 ~ 2))
         )

# format final compiled DO data
dodata <- p %>%
  filter(FLAG_DO == 0) %>%
  mutate(day = yday(datetime),
         month = month(datetime),
         hour = hour(datetime),
         minute = minute(datetime),
         dtime = hour + minute/60,
         do_adj2 = case_when((is.na(do)==F & is.na(do_adj)==T) ~
                               do,
                             TRUE ~ do_adj),
         adj = case_when(is.na(do_adj)==F ~ 1,
                         TRUE ~ 0)) %>%
  select(-do, -do_adj) %>%
  rename(do = do_adj2) %>%
  # right_join(expand.grid(site = unique(p$site), 
  #                        year = 2016:2021, day = 82:339)) %>%
  arrange(site, year, day) %>%
    # Dates based on Anthony V. and shad reference he provided
  mutate(season = case_when(day %in% 105:135 ~ "migrate", #4/15-5/15
                            day %in% 136:151 ~ "spawn", #5/16-5/31
                            day %in% 152:181 ~ "larvae", #6/1-6/30
                            day %in% 182:258 ~ "juvenile", #7/1-9/15
                            day %in% 259:334 ~ "fall_mig"), #9/15-11
         yearf = as.factor(year),
         dayf = as.factor(day),
         hourf = as.factor(hour))

coldo <- dodata %>%
  filter(site %in% c("TNC_23", "TNC_25", 
                     "TNC_24", "TNC_81", "TNC_80")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_do = mean(do),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_do = mean(mean_do),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_do") %>%
  mutate(d25.23 = TNC_25-TNC_23,
         d25.80 = TNC_25-TNC_80,
         d25.81 = TNC_25-TNC_81,
         stage = as.factor(case_when(yearf %in% 2016:2017 ~ 1,
                           yearf == 2018 & as.numeric(as.character(monthf))<7~1,
                           yearf == 2018 & as.numeric(as.character(monthf))>=7 |
                             yearf == 2019 & as.numeric(as.character(monthf))<5~2,
                           yearf == 2019 & as.numeric(as.character(monthf))>=5~3,
                           yearf %in% 2020:2051 ~ 3))
         )

# Tree planting area - DO
    # upstream: TNC_4, within: TNC_5, downstream: TNC_8
treedo <- dodata %>%
  filter(site %in% c("TNC_4", "TNC_5", "TNC_8")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_do = mean(do),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_do = mean(mean_do),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_do") %>%
  mutate(d8.4 = TNC_8-TNC_4,
         d5.4 = TNC_5-TNC_4,
         d4.8 = TNC_4-TNC_8,
         d4.5 = TNC_4-TNC_5,
         stage = as.factor(case_when(yearf %in% 2016:2018 ~ 1,
                           yearf %in% 2019:2051 ~ 2))
         )


# turbidity data
# note: flag counts were as follower prior to filtering
#      0    1.5      2      5      8 
# 214779    188  33345  13893    340 
turb <- p %>%
  filter(is.na(turb) == F,
         FLAG_NTU == 0) %>%
    mutate(day = yday(datetime),
         month = month(datetime),
         hour = hour(datetime),
         minute = minute(datetime),
         dtime = hour + minute/60) %>%
  arrange(site, year, day) %>%
  mutate(yearf = as.factor(year),
         dayf = as.factor(day),
         hourf = as.factor(hour))

# summarize turbidity data for columbia dam
 colturb <- turb %>%
  filter(site %in% c("TNC_23", "TNC_25", 
                     "TNC_24", "TNC_81", "TNC_80")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_turb = mean(turb),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_turb = mean(mean_turb),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_turb") %>%
  mutate(d25.23 = log(TNC_25)-log(TNC_23),
         d25.80 = log(TNC_25)-log(TNC_80),
         d25.81 = log(TNC_25)-log(TNC_81),
         stage = as.factor(case_when(yearf %in% 2016:2017 ~ 1,
                           yearf == 2018 & as.numeric(as.character(monthf))<7~1,
                           yearf == 2018 & as.numeric(as.character(monthf))>=7 |
                             yearf == 2019 & as.numeric(as.character(monthf))<5~2,
                           yearf == 2019 & as.numeric(as.character(monthf))>=5~3,
                           yearf %in% 2020:2051 ~ 3))
         )

 
# Paulina Dam - Temperature
    # upstream: TNC_18, downstream: TNC_19
pault <- tdata %>%
  filter(site %in% c("TNC_18", "TNC_19")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_temp = mean(temp),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_temp = mean(mean_temp),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_temp") %>%
  mutate(d19.18 = TNC_19-TNC_18)
         

# Paulina Dam - DO
    # upstream: TNC_18, downstream: TNC_19
pauldo <- dodata %>%
  filter(site %in% c("TNC_18", "TNC_19")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_do = mean(do),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_do = mean(mean_do),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_do") %>%
  mutate(d19.18 = TNC_19-TNC_18)

# Paulina Dam - turbidity
    # upstream: TNC_18, downstream: TNC_19
paulturb <- turb %>%
  filter(site %in% c("TNC_18", "TNC_19")) %>%
  mutate(monthf = as.factor(month)) %>%
    group_by(site, yearf, monthf, dayf, hourf) %>%
  summarize(mean_turb = mean(turb),
            .groups = "drop") %>%
  group_by(site, yearf, monthf, dayf) %>%
  summarize(mean_turb = mean(log(mean_turb)),
            .groups = "drop") %>%
  tidyr::pivot_wider(names_from = "site", 
                     values_from = "mean_turb") %>%
  mutate(d19.18 = TNC_19-TNC_18)

rm(p)
```
# 3.1. Plot A: Columbia Dam - Temperature upstream vs. downstream - raw data by year
Upstream site = TNC_23; Downstream site = TNC_25 (& 24); Sites within the former impoundment = TNC_80 & TNC_81. First notch in the dam made in July 2018, removal completed April 2019.
```{r}
col %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "steelblue")  +
  geom_boxplot(aes(y = d25.23, x = yearf), 
               fill = "steelblue", alpha = 0.5,
               color = "steelblue"
              ) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Temp. difference (C)\n(downstream - upstream)",
       title = "Columbia Dam") 


ggsave(here::here("output/Task3_project_impacts/",
                  "PlotA_columbia_up_downstream_diff_by_year.png"),
                  height = 4, width = 6, dpi = 400)

```
# 3.2. Plot B: assessing variability in upstream/downstream temp diff by month/year
```{r}
col %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "steelblue")  +
  geom_boxplot(aes(x = monthf, 
                y = d25.23), 
               color = "steelblue", fill = "steelblue",
               alpha = 0.5) +
  facet_wrap(~yearf) + 
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "Temp. difference (C)\n(downstream - upstream)",
       title = "Columbia Dam") +
  scale_x_discrete(breaks = c(3,6,9,12),
                     labels = c("Mar","Jun","Sep","Dec"))
  
ggsave(here::here("output/Task3_project_impacts/",
                  "PlotB_columbia_up_downstream_diff_by_year.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.3. Model A: Columbia Dam downstream/upstream BACI - by stage
Upstream site = TNC_23; Downstream site = TNC_25
```{r}

# format temperature data of Columbia Dam site for JAGS
colt_jags <- col %>% 
  filter(is.na(d25.23) == F,
         monthf %in% 4:11) %>%
  droplevels()

colt_jags_data <- list(
  N = nrow(colt_jags),
  tdiff = colt_jags$d25.23,
  stage = as.numeric(as.character(colt_jags$stage)),
  year = as.numeric(colt_jags$yearf),
  month = as.numeric(as.character(colt_jags$monthf)),
  cov.mat = as.matrix(
    model.matrix(d25.23 ~ stage + monthf ,
                 data = colt_jags)[, c(2:10)]
  )
)

cat(file = "scripts/columbia_baci.txt", 
"
model{

  # likelihood
  for( i in 1:N ){
  tdiff[i] ~ dnorm(mu[i], tau[stage[i]])
  mu[i] <- beta0 + inprod(beta.cov[], cov.mat[i,])

  }
  
  # priors
  beta0 ~ dnorm(0, 1.0E-06)
  
  for( s in 1:3 ) {
  tau[s] ~ dgamma(1, 1)
  }
  
  for( m in 1:9 ){ 
  beta.cov[m] ~ dnorm(0, 1.0E-06)
  }
  
  # derrived
  mean_month <- (0+beta.cov[3]+beta.cov[4]+beta.cov[5]+beta.cov[6]+beta.cov[7]+beta.cov[8])/7
  
  mean_pre <- beta0 + mean_month
  mean_dur <- beta0 + beta.cov[1] + mean_month
  mean_post <- beta0 + beta.cov[2] + mean_month
  ba_diff <- mean_post - mean_pre

  for(s in 1:3){
  sigma[s] <- pow(tau[s], -0.5)
  }
  
}
"
)

colt_jags_mod <- jagsUI::jags(data = colt_jags_data,
             model.file = "scripts/columbia_baci.txt",
             n.iter = 3000, n.burnin = 1000,
             parameters.to.save = c("mean_pre",
                                    "mean_dur",
                                    "mean_post",
                                    "ba_diff",
                                    "beta0",
                                    "beta.cov",
                                    "sigma",
                                    "tau",
                                    "mean_month"),
             n.chains = 3, parallel = T, n.thin = 1
             ); colt_jags_mod

# DIC w/ month: ~500 
    # w/o month: ~550
# dev.new(6,6);plot(colt_jags_mod)


# jagsUI::traceplot(colt_jags_mod)

saveRDS(colt_jags_mod, here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelA_columbia_jags_tmod.rds"))
```
# 3.4. Plot C: estimated upstream/downstream tdiff by restoration stage
```{r}

col_jags_tmod_ni <- readRDS(here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelA_columbia_jags_tmod.rds"))

col_tdiff_plot <- 
  data.frame(draws = col_jags_tmod_ni$sims.list$mean_pre,
           var = "Before\nremoval") %>%
  bind_rows(
    data.frame(draws = col_jags_tmod_ni$sims.list$mean_dur,
           var = "During\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_tmod_ni$sims.list$mean_post,
           var = "After\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_tmod_ni$sims.list$ba_diff,
           var = "change")) %>%
  group_by(var) %>%
  summarise(mu = mean(draws),
            q2.5 = quantile(draws, 0.025),
            q10 = quantile(draws, 0.1),
            q50 = quantile(draws, 0.5),
            q90 = quantile(draws, 0.9),
            q97.5 = quantile(draws, 0.975)) %>%
  mutate(order = c(3,1,4,2),
         var = fct_reorder(var, order))

col_tdiff_plot %>%
  filter(var != "change") %>%
  ggplot() +
  geom_line(aes(x = var, y = mu, group = 1), 
            size = .75, lty = 2) +
  geom_errorbar(aes(x = var, ymin = q10, 
                    ymax = q90), width = 0, size = 1.5) +
  geom_errorbar(aes(x = var, ymin = q2.5, 
                    ymax = q97.5), width = 0, size = .75) +
  geom_point(aes(x = var, y = mu), size = 4) +

  theme_bw() +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) + 
  annotate("text", x = 2.95, y = .46, 
           label = "Change = -0.33C\n(95% CI = -0.41, -0.25)",
           hjust = .5, color = "darkgray", size = 5) +  
  scale_y_continuous(limits = c(-0.05, 0.5)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") + 
  labs(x = "", 
       y = "Temperature difference (C)\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotC_columbia_river_temp_BACI_plot.png"),
                  height = 4, width = 6, dpi = 400)
  
```
# 3.5. Plot D: estimated variability in upstream/downstream temp diff by restoration stage
Did the standard deviation (variability) of the upstream/downstream difference change pre- / post-restoration?
```{r}

col_jags_tmod_ni <- readRDS(here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelA_columbia_jags_tmod.rds"))

col_tdiff_plot_sd <- 
  data.frame(draws = col_jags_tmod_ni$sims.list$sigma[,1],
           var = "Before\nremoval") %>%
  bind_rows(
    data.frame(draws = col_jags_tmod_ni$sims.list$sigma[,2],
           var = "During\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_tmod_ni$sims.list$sigma[,3],
           var = "After\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_tmod_ni$sims.list$ba_diff,
           var = "change")) %>%
  group_by(var) %>%
  summarise(mu = mean(draws),
            q2.5 = quantile(draws, 0.025),
            q10 = quantile(draws, 0.1),
            q50 = quantile(draws, 0.5),
            q90 = quantile(draws, 0.9),
            q97.5 = quantile(draws, 0.975)) %>%
  mutate(order = c(3,1,4,2),
         var = fct_reorder(var, order))

col_tdiff_plot_sd %>%
  filter(var != "change") %>%
  ggplot() +
  geom_line(aes(x = var, y = mu, group = 1), 
            size = .75, lty = 2) +
  geom_errorbar(aes(x = var, ymin = q10, 
                    ymax = q90), width = 0, size = 1.5) +
  geom_errorbar(aes(x = var, ymin = q2.5, 
                    ymax = q97.5), width = 0, size = .75) +
  geom_point(aes(x = var, y = mu), size = 4) +

  theme_bw() +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) + 
  scale_y_continuous(limits = c(0.1, 0.8)) +
  labs(x = "", 
       y = "Std. dev. temperature difference (C)\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotD_columbia_river_temp_SD_BACI_plot.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.6. Plot E: Columbia Dam - DO upstream vs. downstream - raw data by year
upstream: TNC_23, downstream: TNC_25 (& 24), in: 80 & 81
first notch July 2018, completed April 2019
```{r}
coldo %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "olivedrab")  +
  geom_boxplot(aes(y = d25.23, x = yearf), 
               fill = "olivedrab", alpha = 0.5,
               color = "olivedrab"
              ) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "DO difference (mg/L)\n(downstream - upstream)",
       title = "Columbia Dam") 


ggsave(here::here("output/Task3_project_impacts/",
                  "PlotE_columbia_up_downstream_DO_diff_by_year.png"),
                  height = 4, width = 6, dpi = 400)

```
# 3.7. Plot F: assessing variability in upstream/downstream DO diff by month/year
```{r}
coldo %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "olivedrab")  +
  geom_boxplot(aes(x = monthf, 
                y = d25.23), 
               color = "olivedrab", fill = "olivedrab",
               alpha = 0.5) +
  facet_wrap(~yearf) + 
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "DO difference (mg/L)\n(downstream - upstream)",
       title = "Columbia Dam") +
  scale_x_discrete(breaks = c(3,6,9,12),
                     labels = c("Mar","Jun","Sep","Dec"))
  
ggsave(here::here("output/Task3_project_impacts/",
                  "PlotF_columbia_up_downstream_DO_diff_by_month_year.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.8. Model B: Columbia Dam downstream/upstream BACI - DO by stage
```{r}

coldo_jags <- coldo %>% 
  filter(is.na(d25.23) == F,
         monthf %in% 4:11) %>%
  droplevels()

coldo_jags_data <- list(
  N = nrow(coldo_jags),
  tdiff = coldo_jags$d25.23,
  stage = as.numeric(as.character(coldo_jags$stage)),
  year = as.numeric(coldo_jags$yearf),
  month = as.numeric(as.character(coldo_jags$monthf)),
  cov.mat = as.matrix(
    model.matrix(d25.23 ~ stage + monthf ,
                 data = coldo_jags)[, c(2:10)]
  )
)

coldo_jags_mod <- jagsUI::jags(data = coldo_jags_data,
             model.file = "scripts/columbia_baci.txt",
             n.iter = 3000, n.burnin = 1000,
             parameters.to.save = c("mean_pre",
                                    "mean_dur",
                                    "mean_post",
                                    "ba_diff",
                                    "beta0",
                                    "beta.cov",
                                    "sigma",
                                    "tau",
                                    "mean_month"),
             n.chains = 3, parallel = T, n.thin = 1
             ); coldo_jags_mod

 # dev.new(6,6); plot(coldo_jags_mod)


# jagsUI::traceplot(coldo_jags_mod)

saveRDS(coldo_jags_mod, here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelB_columbia_jags_domod.rds"))
```
# 3.9. Plot F: estimated upstream/downstream DO diff by restoration stage
```{r}

coldo_jags_mod <- readRDS(here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelB_columbia_jags_domod.rds"))

coldo_diff_plot <- 
  data.frame(draws = coldo_jags_mod$sims.list$mean_pre,
           var = "Before\nremoval") %>%
  bind_rows(
    data.frame(draws = coldo_jags_mod$sims.list$mean_dur,
           var = "During\nremoval")) %>%
  bind_rows(
  data.frame(draws = coldo_jags_mod$sims.list$mean_post,
           var = "After\nremoval")) %>%
  bind_rows(
  data.frame(draws = coldo_jags_mod$sims.list$ba_diff,
           var = "change")) %>%
  group_by(var) %>%
  summarise(mu = mean(draws),
            q2.5 = quantile(draws, 0.025),
            q10 = quantile(draws, 0.1),
            q50 = quantile(draws, 0.5),
            q90 = quantile(draws, 0.9),
            q97.5 = quantile(draws, 0.975)) %>%
  mutate(order = c(3,1,4,2),
         var = fct_reorder(var, order))

coldo_diff_plot %>%
  filter(var != "change") %>%
  ggplot() +
  geom_line(aes(x = var, y = mu, group = 1), 
            size = .75, lty = 2) +
  geom_errorbar(aes(x = var, ymin = q10, 
                    ymax = q90), width = 0, size = 1.5) +
  geom_errorbar(aes(x = var, ymin = q2.5, 
                    ymax = q97.5), width = 0, size = .75) +
  geom_point(aes(x = var, y = mu), size = 4) +

  theme_bw() +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) + 
  annotate("text", x = 2.95, y = .4, 
           label = "Change = +0.18mg/L\n(95% CI = 0.08, 0.27)",
           hjust = .5, color = "darkgray", size = 5) +  
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") + 
  labs(x = "", 
       y = "DO difference (mg/L)\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotG_columbia_river_DO_BACI_plot.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.10. Plot H: estimated variability (SD) in upstream/downstream DO diff by restoration stage
```{r}

coldo_jags_mod <- readRDS(here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelB_columbia_jags_domod.rds"))

coldo_diff_plot_sd <- 
  data.frame(draws = coldo_jags_mod$sims.list$sigma[,1],
           var = "Before\nremoval") %>%
  bind_rows(
    data.frame(draws = coldo_jags_mod$sims.list$sigma[,2],
           var = "During\nremoval")) %>%
  bind_rows(
  data.frame(draws = coldo_jags_mod$sims.list$sigma[,3],
           var = "After\nremoval")) %>%
  bind_rows(
  data.frame(draws = coldo_jags_mod$sims.list$ba_diff,
           var = "change")) %>%
  group_by(var) %>%
  summarise(mu = mean(draws),
            q2.5 = quantile(draws, 0.025),
            q10 = quantile(draws, 0.1),
            q50 = quantile(draws, 0.5),
            q90 = quantile(draws, 0.9),
            q97.5 = quantile(draws, 0.975)) %>%
  mutate(order = c(3,1,4,2),
         var = fct_reorder(var, order))

coldo_diff_plot_sd %>%
  filter(var != "change") %>%
  ggplot() +
  geom_line(aes(x = var, y = mu, group = 1), 
            size = .75, lty = 2) +
  geom_errorbar(aes(x = var, ymin = q10, 
                    ymax = q90), width = 0, size = 1.5) +
  geom_errorbar(aes(x = var, ymin = q2.5, 
                    ymax = q97.5), width = 0, size = .75) +
  geom_point(aes(x = var, y = mu), size = 4) +

  theme_bw() +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) + 
  # annotate("text", x = 2.95, y = .6, 
  #          label = "Change = +0.18mg/L\n(95% CI = 0.08, 0.27)",
  #          hjust = .5, color = "darkgray", size = 5) +  
  # geom_hline(yintercept = 0, lty = 2, color = "darkgray") + 
  scale_y_continuous(limits = c(0.4,0.8)) +
  labs(x = "", 
       y = "Std. dev. of DO difference (mg/L)\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotH_columbia_river_DO_SD_BACI_plot.png"),
                  height = 4, width = 6, dpi = 400)
  
```
# 3.11. Plot I: Tree planting - upstream/downstream temp diff by month/year
```{r}
tree %>%
  filter(#yearf != 2016,
         monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d8.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Temp. difference (C)\n(downstream - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1) +
 scale_y_continuous(limits = c(-0.5, 1.5))
  
ggsave(here::here("output/Task3_project_impacts/",
                  "PlotI_tree_planting_up_downstream_diff_by_mo_year.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.12. Plot J: Tree planting - upstream/within temp diff by month/year
```{r}
tree %>%
  filter(monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d5.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  # geom_smooth(aes(x = yearf, y = val, color = mo, group = mo), 
  #             method = "lm", 
  #             se = F, size = .5) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Temp. difference (C)\n(restoration area - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1) +
  scale_y_continuous(limits = c(-0.5, 1.5))
  
ggsave(here::here("output/Task3_project_impacts/",
                "PlotJ_trees_up_vs_within_diff_by_mo_year.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.13. Plot K: Tree planting - downstream & within, raw temp by month/year
```{r}
tree %>%
  filter(monthf %in% 5:9) %>%
  droplevels() %>%
  select(yearf, monthf, TNC_5, TNC_8) %>%
  pivot_longer(cols = c(TNC_5, TNC_8), names_to = "site",
               values_to = "val1") %>%
  group_by(yearf, monthf, site) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  facet_wrap(~site) +
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "Mean temperature (C)\n+/- 2 SE",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1)
  
ggsave(here::here("output/Task3_project_impacts/",
                "PlotK_trees_down_vs_within_temp_by_mo_year.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.14. Model C: Tree planting temperature trend (downstream - upstream)
TNC_8 - TNC_4; Model to estimate mean trend. Then use to redo plot I showing trend info.
```{r}
treet_jags <- tree %>% 
  filter(is.na(d8.4) == F,
         monthf %in% 5:9) %>%
  droplevels()

treet_jags_data <- list(
  N = nrow(treet_jags),
  n_yr = length(unique(treet_jags$yearf)),
  tdiff = treet_jags$d8.4,
  year_mean = mean(as.numeric(treet_jags$yearf)),
  stage = as.numeric(as.character(treet_jags$stage)),
  year = as.numeric(treet_jags$yearf),
  month = as.numeric(as.character(treet_jags$monthf))
)

cat(file = "scripts/tree_trend.txt", 
"
model{

  # likelihood
  for( i in 1:N ){
  tdiff[i] ~ dnorm(mu[i], pow(sigma, -2))
  mu[i] <- beta0[month[i]] + beta.year[month[i]]*(year[i]-year_mean)
  }
  
  # hyper priors
  for(i in 5:9){
  beta0[i] ~ dnorm(mu.beta0, pow(sigma.beta0, -2))
  beta.year[i] ~ dnorm(mu.beta.year, pow(sigma.beta.year, -2))
  }
  
  # priors
  sigma ~ dunif(0, 50)
  mu.beta0 ~ dnorm(0, 1.0E-06)
  mu.beta.year ~ dnorm(0, 1.0E-06)
  sigma.beta0 ~ dunif(0, 50)
  sigma.beta.year ~ dunif(0, 50)

  # derrived
  for(i in 1:n_yr){
  diff_pred[i] <- mu.beta0 + mu.beta.year*(i-year_mean)
  }
  
}
"
)

treet_jags_mod <- jagsUI::jags(data = treet_jags_data,
             model.file = "scripts/tree_trend.txt",
             n.iter = 10000, n.burnin = 4000,
             parameters.to.save = c("mu.beta0",
                                    "mu.beta.year",
                                    "beta0",
                                    "beta.year",
                                    "sigma",
                                    "tau",
                                    "tau.beta0",
                                    "tau.beta.year",
                                    "sigma.beta0",
                                    "sigma.beta.year",
                                    "diff_pred"),
             n.chains = 3, parallel = T, n.thin = 3
             ); treet_jags_mod

# dev.new(6,6);plot(treet_jags_mod)

saveRDS(treet_jags_mod, 
        here(task_path,
             "statistical_analysis/",
             "ModelC_tree_planting_temperature_trends_down_up.rds")
)
```
# 3.15. Plot I2: tree planting area down vs. upstream temperature modeled mean trend (downstream - upstream)
TNC_8 - TNC_4
Model to estimate mean temperature trend. Redo of plot I showing trend info.
```{r}
# load JAGS data
treet_jags <- tree %>% 
  filter(is.na(d8.4) == F,
         monthf %in% 5:9) %>%
  droplevels()

# get max year
max_yr <- max(as.numeric(as.character(treet_jags$yearf)))

# load JAGS model results object
treet_jags_mod <- readRDS(here(task_path,
             "statistical_analysis/",
             "ModelC_tree_planting_temperature_trends_down_up.rds"))

# get trend, LCI, and UCI
trend <- round(treet_jags_mod$mean$mu.beta.year, 2)
lci <- round(treet_jags_mod$q2.5$mu.beta.year, 2)
uci <- round(treet_jags_mod$q97.5$mu.beta.year, 2)

# format data for plotting
treet_jags_plot <- 
  apply(treet_jags_mod$sims.list$diff_pred, 2, 
        function(x) quantile(x, c(0.025, 0.1, 0.5, 0.90, 0.975))) %>%
  t() %>%
  as.data.frame() %>%
  rename(q2.5 = 1, q10 = 2, med = 3, q90 = 4, q97.5 = 5) %>%
  mutate(year = 2016:max_yr) 

# make the plot
tree %>%
  filter(monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d8.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  geom_line(aes(x = as.factor(year), y = med, 
                group = 1), size = 1, 
            data = treet_jags_plot) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Temp. difference (C)\n(downstream - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1) +
 scale_y_continuous(limits = c(-0.5, 1.5)) +
  annotate("text", x = max(as.numeric(treet_jags$yearf)), y = -0.49, 
           label = paste0("mean trend = ",
                          trend, " C/yr\n95% CI = ", 
                          lci, ", ", uci), 
           hjust = 1, vjust = 0)

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotI2_trees_up_vs_down_diff_by_mo_trend.png"),
                  height = 5, width = 7, dpi = 400)

```
# 3.16. Model D: Tree planting temperature trend (within - upstream)
TNC_5 - TNC_4. Model to estimate mean trend.
```{r}
treet_jags <- tree %>% 
  filter(is.na(d5.4) == F,
         monthf %in% 5:9) %>%
  droplevels()

treet_jags_data <- list(
  N = nrow(treet_jags),
  n_yr = length(unique(treet_jags$yearf)),
  tdiff = treet_jags$d5.4,
  year_mean = mean(as.numeric(treet_jags$yearf)),
  stage = as.numeric(as.character(treet_jags$stage)),
  year = as.numeric(treet_jags$yearf),
  month = as.numeric(as.character(treet_jags$monthf))
)

treet_jags_mod2 <- jagsUI::jags(data = treet_jags_data,
             model.file = "scripts/tree_trend.txt",
             n.iter = 10000, n.burnin = 4000,
             parameters.to.save = c("mu.beta0",
                                    "mu.beta.year",
                                    "beta0",
                                    "beta.year",
                                    "sigma",
                                    "tau",
                                    "tau.beta0",
                                    "tau.beta.year",
                                    "sigma.beta0",
                                    "sigma.beta.year",
                                    "diff_pred"),
             n.chains = 3, parallel = T, n.thin = 3
             ); treet_jags_mod2

# dev.new(6,6);plot(treet_jags_mod2)

saveRDS(treet_jags_mod2, 
        here(task_path,
             "statistical_analysis/",
             "ModelD_tree_planting_temp_trends_within_up.rds")
)
```
# 3.17. Plot J2: tree planting temperature trend (within - upstream)
TNC_5 - TNC_4
Model to estimate mean trend. Redo plot J showing trend info.
```{r}
# load the jags data
treet_jags <- tree %>% 
  filter(is.na(d5.4) == F,
         monthf %in% 5:9) %>%
  droplevels()

# get max year
max_yr <- max(as.numeric(as.character(treet_jags$yearf)))

# load JAGS model results object
treet_jags_mod <- readRDS(here(task_path,
             "statistical_analysis/",
             "ModelD_tree_planting_temp_trends_within_up.rds"))

# get trend, LCI, and UCI
trend <- round(treet_jags_mod$mean$mu.beta.year, 2)
lci <- round(treet_jags_mod$q2.5$mu.beta.year, 2)
uci <- round(treet_jags_mod$q97.5$mu.beta.year, 2)



treet_jags_plot <- apply(treet_jags_mod2$sims.list$diff_pred, 2, function(x) quantile(x, c(0.025, 0.1, 0.5, 0.90, 0.975))) %>%
  t() %>%
  as.data.frame() %>%
  rename(q2.5 = 1, q10 = 2, med = 3, q90 = 4, q97.5 = 5) %>%
  mutate(year = 2016:max_yr) 

tree %>%
  filter(monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d5.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  geom_line(aes(x = as.factor(year), y = med, 
                group = 1), size = 1, 
            data = filter(treet_jags_plot, year != 2017)) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Temp. difference (C)\n(restoration area - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2017,2019,2021)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1) +
  scale_y_continuous(limits = c(-0.5, 1.5)) +
  annotate("text", x = max(as.numeric(treet_jags$yearf)), y = -0.49, 
           label = paste0("mean trend = ",
                          trend, " C/yr\n95% CI = ", 
                          lci, ", ", uci), 
           hjust = 1, vjust = 0)

ggsave(here::here("output/Task3_project_impacts/",
                "PlotJ2_trees_up_vs_within_diff_by_mo_trend.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.18. Plot L: Tree planting - upstream/downstream DO diff by month/year
TNC_8 (downstream) - TNC_4 (upstream)
```{r}
treedo %>%
  filter(is.na(d8.4)==F,
         monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d8.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "DO difference (mg/L)\n(downstream - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1)
  
ggsave(here::here("output/Task3_project_impacts/",
                  "PlotL_trees_up_vs_downstream_DO_diff_by_mo.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.19. Plot M: Tree planting - upstream/within DO diff by month/year
```{r}
treedo %>%
  filter(is.na(d5.4)==F,
         monthf %in% 5:9) %>%
  droplevels() %>%
  rename(val1 = d5.4) %>%
  group_by(yearf, monthf) %>%
  summarise(val = mean(val1, na.rm = T),
            sd = sd(val1, na.rm = T),
            n = length(is.na(val1)),
            se = sd/sqrt(n)) %>%
  mutate(mo = case_when(monthf == 5 ~ "May",
                        monthf == 6 ~ "Jun",
                        monthf == 7 ~ "Jul",
                        monthf == 8 ~ "Aug",
                        monthf == 9 ~ "Sep"),
         mo = fct_reorder(mo, as.numeric(monthf))) %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, 
              lty = 2, color = "darkgray")  +
  geom_line(aes(x = yearf,
                y = val, color = mo,
                group = monthf),
               size = .75, lty = 1) +
  geom_point(aes(x = yearf, 
                y = val, 
                color = mo), 
               size = 4) +
  geom_errorbar(aes(x = yearf, 
                ymin = val-2*se, ymax = val+2*se,
                color = mo), 
               size = 1, width = 0) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "DO difference (mg/L)\n(restoration area - upstream)",
       title = "Tree planting area",
       color = "Month") +
  scale_x_discrete(breaks = c(2016:2050)) + 
  scale_color_manual(values = wes_palettes$Darjeeling1)
  
ggsave(here::here("output/Task3_project_impacts/",
                "PlotM_trees_up_vs_within_DOdiff_by_mo.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.20. Plot N: Columbia Dam - Turbidity upstream vs. downstream - raw data by year
Upstream: TNC_23, downstream: TNC_25 (& 24), in: 80 & 81
first notch July 2018, completed April 2019
```{r}
colturb %>%
  select(yearf, value = TNC_25) %>%
  bind_rows(select(rename(colturb, value = TNC_23), yearf, value)) %>%
  mutate(site = c(rep("Downstream", 891), rep("Upstream", 891))) %>%
  ggplot() +
  geom_boxplot(aes(y = value, x = yearf, fill = site, color = site), 
               alpha = 0.5
              ) +
  theme_bw() +
  scale_y_log10() +
  scale_fill_manual(values = c("firebrick", "steelblue")) +
  scale_color_manual(values = c("firebrick", "steelblue")) +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Turbidity (NTU)",
       title = "Columbia Dam", fill = "", color = "") 

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotN_columbia_turbidity_up_downstream_by_year.png"),
                  height = 4, width = 6, dpi = 400)

```
# 3.21. Plot O: Columbia Dam - log turbidity difference, upstream vs. downstream - raw data by year
upstream: TNC_23, downstream: TNC_25 (& 24), in: 80 & 81
first notch July 2018, completed April 2019
```{r}
colturb %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "firebrick")  +
  geom_boxplot(aes(y = d25.23, x = yearf), 
               fill = "firebrick", alpha = 0.5,
               color = "firebrick"
              ) +
  theme_bw() +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Difference in log turbitity (NTU)\n(downstream - upstream)",
       title = "Columbia Dam") 

ggsave(here::here("output/Task3_project_impacts/",
          "PlotO_columbia_turbitity_up_downstream_diff_by_year.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.22. Plot P: assessing variability in upstream/downstream turbidity by month/year
```{r}
colturb %>%
  ggplot() +
  geom_abline(intercept = 0, slope = 0, lty = 3, color = "steelblue")  +
  geom_boxplot(aes(x = monthf, 
                y = d25.23), 
               color = "steelblue", fill = "steelblue",
               alpha = 0.5) +
  facet_wrap(~yearf) + 
  theme_bw() +
  theme(text = element_text(size = 14),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "Difference in log turbidity (NTU)\n(downstream - upstream)",
       title = "Columbia Dam") +
  scale_x_discrete(breaks = c(3,6,9,12),
                     labels = c("Mar","Jun","Sep","Dec"))
  
ggsave(here::here("output/Task3_project_impacts/",
        "PlotP_columbia_turbitity_up_downstream_diff_by_year_mo.png"),
                  height = 5, width = 7, dpi = 400)
```
# 3.23. Model E: Columbia Dam Turbidity - downstream/upstream BACI - by stage
Upstream: TNC_23; Downstream: TNC_25
```{r}
colturb_jags <- colturb %>% 
  filter(is.na(d25.23) == F,
         monthf %in% 4:11) %>%
  droplevels()

colturb_jags_data <- list(
  N = nrow(colturb_jags),
  tdiff = colturb_jags$d25.23,
  stage = as.numeric(as.character(colturb_jags$stage)),
  year = as.numeric(colturb_jags$yearf),
  month = as.numeric(as.character(colturb_jags$monthf)),
  cov.mat = as.matrix(
    model.matrix(d25.23 ~ stage + monthf ,
                 data = colturb_jags)[, c(2:10)]
  )
)

colturb_jags_mod <- jagsUI::jags(data = colturb_jags_data,
             model.file = "scripts/columbia_baci.txt",
             n.iter = 3000, n.burnin = 1000,
             parameters.to.save = c("mean_pre",
                                    "mean_dur",
                                    "mean_post",
                                    "ba_diff",
                                    "beta0",
                                    "beta.cov",
                                    "sigma",
                                    "tau",
                                    "mean_month"),
             n.chains = 3, parallel = T, n.thin = 1
             ); colturb_jags_mod

dev.new(6,6);plot(colturb_jags_mod)


# jagsUI::traceplot(colturb_jags_mod)

saveRDS(colturb_jags_mod, here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelE_columbia_jags_turbmod.rds"))
```
# 3.24. Plot Q: estimated upstream/downstream tdiff by restoration stage
```{r}
col_jags_turbmod_ni <- readRDS(here::here("output/Task3_project_impacts/",
                            "statistical_analysis/",
                          "ModelE_columbia_jags_turbmod.rds"))

col_turbdiff_plot <- 
  data.frame(draws = col_jags_turbmod_ni$sims.list$mean_pre,
           var = "Before\nremoval") %>%
  bind_rows(
    data.frame(draws = col_jags_turbmod_ni$sims.list$mean_dur,
           var = "During\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_turbmod_ni$sims.list$mean_post,
           var = "After\nremoval")) %>%
  bind_rows(
  data.frame(draws = col_jags_turbmod_ni$sims.list$ba_diff,
           var = "change")) %>%
  group_by(var) %>%
  summarise(mu = mean(draws),
            q2.5 = quantile(draws, 0.025),
            q10 = quantile(draws, 0.1),
            q50 = quantile(draws, 0.5),
            q90 = quantile(draws, 0.9),
            q97.5 = quantile(draws, 0.975)) %>%
  mutate(order = c(3,1,4,2),
         var = fct_reorder(var, order))

col_turbdiff_plot %>%
  filter(var != "change") %>%
  ggplot() +
  geom_line(aes(x = var, y = mu, group = 1), 
            size = .75, lty = 2) +
  geom_errorbar(aes(x = var, ymin = q10, 
                    ymax = q90), width = 0, size = 1.5) +
  geom_errorbar(aes(x = var, ymin = q2.5, 
                    ymax = q97.5), width = 0, size = .75) +
  geom_point(aes(x = var, y = mu), size = 4) +

  theme_bw() +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) + 
  annotate("text", x = 2.95, y = 1.46, 
           label = "Change = +0.05\n(95% CI = -0.13, 0.22)",
           hjust = .5, color = "darkgray", size = 5) +  
  # scale_y_continuous(limits = c(-0.05, 0.5)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") + 
  labs(x = "", 
       y = "Difference in log turbidity (NTU)\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotQ_columbia_river_turb_BACI_plot.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.25. Plot R: Paulina Dam - Temperature
Sites TNC_18 and TNC_19.
Note for adding additional years of data: you should update the numbers in this section to reflect new data: "Monthly mean:\n0.3 C warmer on average\nRange: 0 - 1.8 C". The new values can be found by running the command: summary(monthly_diff$diff)
That appears near the bottom of the code chunk just before the ggsave command.
```{r}
# summarize daily temp data by month
tsum_paulina <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(site %in% c("TNC_18", "TNC_19")) %>%
  mutate(site = case_when(site == "TNC_18" ~ "Upstream",
                          site == "TNC_19" ~ "Downstream"))

tsum_envelope <- tdata %>%
  group_by(site, day) %>%
  summarize(multi_min = min(temp),
            multi_max = max(temp),
            .groups = "drop") %>%
  filter(site %in% c("TNC_18", "TNC_19")) %>%
  mutate(site = case_when(site == "TNC_18" ~ "Upstream",
                          site == "TNC_19" ~ "Downstream"))

tsum_paulina %>%
  ggplot() +
  geom_ribbon(aes(x = day, ymax = multi_max,
                  ymin = multi_min), 
              data = filter(tsum_envelope),
              fill = "gray", alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, color = yearf), size = .5,
             shape = 16,
             position = position_dodge(width = 10)) +      
  geom_point(aes(x = mid, y = mean_mean, color = yearf), size = 2,
             shape = 16,
             position = position_dodge(width = 10)) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature",
       title = "Paulina Dam", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,32)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(82, 339),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  scale_color_manual(values = c(wes_palettes$Royal1,
                                wes_palettes$Royal2)) +
  facet_wrap(~site) +
  geom_text(aes(x = mid, y = mean_mean, label = mes),
            hjust = 0, size = 3, vjust = 0,
            color = "darkgray",
                       data = data.frame(mid = c(100,100),
                                         mean_mean = c(0.5,0.5),
    mes = c("Monthly mean:\n0.3 C warmer on average\nRange: 0 - 1.8 C", 
            ""),
                                         site = c("Downstream",
                                                  "Upstream")))

monthly_diff <- data.frame(diff = (filter(tsum_paulina, site == "Downstream")$mean_mean -
  filter(tsum_paulina, site == "Upstream")$mean_mean),
    month = filter(tsum_paulina, site == "Downstream")$month,
  year = filter(tsum_paulina, site == "Downstream")$yearf,
  n = filter(tsum_paulina, site == "Downstream")$n
) %>% 
  filter(n>=10)

summary(monthly_diff$diff)

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotR_paulina_dam_upstream_ds_temp.png"),
                  height = 4, width = 6.5, dpi = 400)
```
# 3.26. Plot S: Paulina downstream (TNC_19) - upstream (TNC_18)
Temp, DO, & Turbidity
```{r}
paulall = mutate(pault, meas = "Temperature") %>%
  bind_rows(mutate(pauldo, meas = "DO")) %>%
  bind_rows(mutate(paulturb, meas = "Turbidity"))

paulall %>%
  group_by(yearf, meas) %>%
  ggplot() +
  geom_boxplot(aes(x = yearf, y = d19.18), 
               color = "steelblue", 
               fill = "skyblue", alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  facet_wrap(~meas, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size = 8),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "Difference\n(downstream - upstream)",
       title = "Paulina Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotS_paulina_dam_upstream_ds_all.png"),
                  height = 4, width = 6.5, dpi = 400)

```
# 3.27. Plot T: Hyper Humus - Temperature & DO
Site TNC_2 compared with other site means.
```{r}
# summarize daily temp data by month
tsum_hyper <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

# summarize daily temp data by month
dosum_hyper <-  dodata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_do = min(do, na.rm = T),
            max_do = max(do, na.rm = T),
            mean_do = mean(do, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_do),
            mean_max = mean(max_do),
            mean_min = mean(min_do),
            n = length(mean_do),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

tsum_hyper %>%
  filter(site == "TNC_2") %>%
  ggplot() +
  geom_line(aes(x = mid, y = mean_mean, #, color = yearf, 
                group = site),
              data = tsum_hyper,
            color = wes_palettes$Royal1[2],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, #, color = yearf, 
                group = site),
              data = dosum_hyper,
            color = wes_palettes$Royal1[1],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean), size = .5,
            color = "black") +      
  geom_point(aes(x = mid, y = mean_mean), size = 2,
             shape = 21, fill = wes_palettes$Royal1[2]) +
  geom_line(aes(x = mid, y = mean_mean), size = .5,
            color = "black",
            data = filter(dosum_hyper, site == "TNC_2")) +      
  geom_point(aes(x = mid, y = mean_mean), size = 2,
             shape = 21, fill = wes_palettes$Royal1[1],
             data = filter(dosum_hyper, site == "TNC_2")) +
  annotate("text", x = 123, y = 24, hjust = 0, 
           label = "Temp.", size = 2.5,
           color = wes_palettes$Royal1[2]) +
  annotate("text", x = 123, y = 2, hjust = 0, 
           label = "DO", size = 2.5,
           color = wes_palettes$Royal1[1]) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature (C)\n or dissolved oxygen (mg/L)",
       title = "Hyper Humus", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,26)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(112, 309),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  facet_wrap(~yearf) +
  guides(fill = "none", color = "none")

ggsave(here::here(task_path,
              "PlotT_hyperhumus_downstream_temp_do.png"),
                  height = 4, width = 6.5, dpi = 400)

rm(tsum_hyper, dosum_hyper)
```
# 3.28. Plot U: County Line Dam - Temperature & DO
TNC_9 and TNC_13 compared with other site means.
```{r}
# summarize daily temp data by month
tsum_county <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

# summarize daily temp data by month
dosum_county <-  dodata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_do = min(do, na.rm = T),
            max_do = max(do, na.rm = T),
            mean_do = mean(do, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_do),
            mean_max = mean(max_do),
            mean_min = mean(min_do),
            n = length(mean_do),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

ggplot() +
  geom_line(aes(x = mid, y = mean_mean, group = site),
              data = tsum_county,
            color = wes_palettes$Royal1[2],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, #, color = yearf, 
                group = site),
              data = dosum_county,
            color = wes_palettes$Royal1[1],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(tsum_county,site %in% c("TNC_9","TNC_13"))) + 
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 2,
             fill = wes_palettes$Royal1[2],
             filter(tsum_county,site %in% c("TNC_9","TNC_13"))) +
  scale_shape_manual(values = c(21, 22)) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(dosum_county, site %in% c("TNC_9",
                                                    "TNC_13"))) +      
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 2,
             fill = wes_palettes$Royal1[1],
             data = filter(dosum_county, site %in% c("TNC_9",
                                                     "TNC_13"))) +
  annotate("text", x = 122.5, y = 24, hjust = 0, 
           label = "Temp.", size = 2,
           color = wes_palettes$Royal1[2]) +
  annotate("text", x = 123, y = 2.75, hjust = 0, 
           label = "DO", size = 2,
           color = wes_palettes$Royal1[1]) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature (C)\n or dissolved oxygen (mg/L)", shape = "Site", lty = "Site",
       title = "County Line Dam", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,26)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(112, 309),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  facet_wrap(~yearf) +
  guides(fill = "none", color = "none")

ggsave(here::here(task_path,
              "PlotU_countyline_dam_downstream_temp_do.png"),
                  height = 3.5, width = 6, dpi = 400)

rm(tsum_county, dosum_county)
```
# 3.29. Plot V: Tree planting area - Temperature & DO
Monthly averages each year for TNC_4, 5, and 8 (compared with other site means)
```{r}
# make a list of the relevant sites
tree.sites <- c("TNC_4", "TNC_5", "TNC_8")

# summarize daily temp data by month
tsum_tree <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

# summarize daily temp data by month
dosum_tree <-  dodata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_do = min(do, na.rm = T),
            max_do = max(do, na.rm = T),
            mean_do = mean(do, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_do),
            mean_max = mean(max_do),
            mean_min = mean(min_do),
            n = length(mean_do),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

ggplot() +
  geom_line(aes(x = mid, y = mean_mean, group = site),
              data = tsum_tree,
            color = wes_palettes$Royal1[2],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, #, color = yearf, 
                group = site),
              data = dosum_tree,
            color = wes_palettes$Royal1[1],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(tsum_tree,site %in% tree.sites)) + 
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 1.5,
             fill = wes_palettes$Royal1[2],
             filter(tsum_tree,site %in% tree.sites)) +
  scale_shape_manual(values = c(21, 22, 23)) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(dosum_tree, site %in% tree.sites)) +      
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 1.5,
             fill = wes_palettes$Royal1[1],
             data = filter(dosum_tree, site %in% tree.sites)) +
  annotate("text", x = 122.5, y = 24, hjust = 0, 
           label = "Temp.", size = 2,
           color = wes_palettes$Royal1[2]) +
  annotate("text", x = 123, y = 2.75, hjust = 0, 
           label = "DO", size = 2,
           color = wes_palettes$Royal1[1]) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature (C)\n or dissolved oxygen (mg/L)", shape = "Site", lty = "Site",
       title = "Tree planting sites", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,26)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(112, 309),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  facet_wrap(~yearf) +
  guides(fill = "none", color = "none")

ggsave(here::here(task_path,
              "PlotV_tree_planting_sites_temp_do.png"),
                  height = 3.5, width = 6, dpi = 400)

rm(tsum_tree, dosum_tree)
```
# 3.30. Plot W: Columbia Dam - Temperature & DO
Monthly averages each year for TNC_4, 5, and 8 (compared with other site means)
```{r}
# make a list of the relevant sites
the.sites <- c("TNC_23", "TNC_25", "TNC_80", "TNC_81")

# summarize daily temp data by month
tsum_col <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

# summarize daily temp data by month
dosum_col <-  dodata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_do = min(do, na.rm = T),
            max_do = max(do, na.rm = T),
            mean_do = mean(do, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_do),
            mean_max = mean(max_do),
            mean_min = mean(min_do),
            n = length(mean_do),
            .groups = "drop") %>%
  filter(n >= 2) %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(month %notin% c(4,11))

ggplot() +
  geom_line(aes(x = mid, y = mean_mean, group = site),
              data = tsum_col,
            color = wes_palettes$Royal1[2],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, #, color = yearf, 
                group = site),
              data = dosum_col,
            color = wes_palettes$Royal1[1],
              alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(tsum_col,site %in% the.sites)) + 
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 1.5,
             fill = wes_palettes$Royal1[2],
             filter(tsum_col,site %in% the.sites)) +
  scale_shape_manual(values = c(21, 22, 23, 24)) +
  geom_line(aes(x = mid, y = mean_mean, group = site,
                lty = site), size = .5,
            color = "black",
            data = filter(dosum_col, site %in% the.sites)) +      
  geom_point(aes(x = mid, y = mean_mean, shape = site), size = 1.5,
             fill = wes_palettes$Royal1[1],
             data = filter(dosum_col, site %in% the.sites)) +
  annotate("text", x = 122.5, y = 24, hjust = 0, 
           label = "Temp.", size = 2,
           color = wes_palettes$Royal1[2]) +
  annotate("text", x = 123, y = 2.75, hjust = 0, 
           label = "DO", size = 2,
           color = wes_palettes$Royal1[1]) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature (C)\n or dissolved oxygen (mg/L)", shape = "Site", lty = "Site",
       title = "Columbia Dam", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,26)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(112, 309),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  facet_wrap(~yearf) +
  guides(fill = "none", color = "none")

ggsave(here::here(task_path,
              "PlotW_Columbia_Dam_sites_temp_do.png"),
                  height = 3.5, width = 6, dpi = 400)

rm(tsum_col, dosum_col)
```
# 3.31. Plot X: Columbia Dam - Temp. upstream vs. downstream - raw data by year
upstream: TNC_23, downstream: TNC_25 (& 24), within former impoundment: 80 & 81; first notch July 2018, completed April 2019
```{r}
col %>%
  select(yearf, value = TNC_25, monthf) %>%
  mutate(site = "Downstream") %>%
  bind_rows(mutate(select(rename(col, value = TNC_23), yearf, value, monthf), site = "Upstream")) %>%
  bind_rows(mutate(select(rename(col, value = TNC_80), yearf, value, monthf), site = "Inside (80)")) %>%
  bind_rows(mutate(select(rename(col, value = TNC_81), yearf, value, monthf), site = "Inside (81)")) %>%
  ggplot() +
  geom_boxplot(aes(y = value, x = yearf, fill = site, color = site), 
               alpha = 0.5
              ) +
  theme_bw() +
  scale_fill_manual(values =
                    c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  scale_color_manual(values = c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Daily mean temperature (C)",
       title = "Columbia Dam", fill = "", color = "") 


ggsave(here::here("output/Task3_project_impacts/",
              "PlotX_columbia_temperature_up_downstream_by_year.png"),
                  height = 4, width = 6, dpi = 400)

```
# 3.32. Plot Y: Columbia Dam - July Temp. upstream vs. downstream - raw data by year
upstream: TNC_23, downstream: TNC_25 (& 24), in: 80 & 81
first notch July 2018, completed April 2019
```{r}
col %>%
  select(yearf, value = TNC_25, monthf) %>%
  mutate(site = "Downstream") %>%
  bind_rows(mutate(select(rename(col, value = TNC_23), yearf, value, monthf), site = "Upstream")) %>%
  bind_rows(mutate(select(rename(col, value = TNC_80), yearf, value, monthf), site = "Inside (80)")) %>%
  bind_rows(mutate(select(rename(col, value = TNC_81), yearf, value, monthf), site = "Inside (81)")) %>%
  filter(monthf==7) %>%
  ggplot() +
  geom_boxplot(aes(y = value, x = yearf, fill = site, color = site), 
               alpha = 0.5
              ) +
  theme_bw() +
  scale_fill_manual(values =
                    c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  scale_color_manual(values = c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Daily mean temperature (C)\nin July",
       title = "Columbia Dam", fill = "", color = "") 


ggsave(here::here("output/Task3_project_impacts/",
                  "Ploty_columbia_July_temperature_up_downstream_by_year.png"),
                  height = 4, width = 6, dpi = 400)

```
# 3.33. Plot Z: Columbia Dam - DO upstream vs. downstream - daily data by year
upstream: TNC_23, downstream: TNC_25 (& 24), within former impoundment: 80 & 81; first notch July 2018, completed April 2019
```{r}
coldo %>%
  select(yearf, value = TNC_25, monthf) %>%
  mutate(site = "Downstream") %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_23), yearf, value, monthf), site = "Upstream")) %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_80), yearf, value, monthf), site = "Inside (80)")) %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_81), yearf, value, monthf), site = "Inside (81)")) %>%
  ggplot() +
  geom_boxplot(aes(y = value, x = yearf, fill = site, color = site), 
               alpha = 0.5
              ) +
  theme_bw() +
  scale_fill_manual(values =
                    c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  scale_color_manual(values = c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Daily mean DO (mg/L)",
       title = "Columbia Dam", fill = "", color = "") 


ggsave(here::here("output/Task3_project_impacts/",
                  "PlotZ_columbia_DO_up_downstream_by_year.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.34. Plot ZA: Columbia Dam - DO upstream vs. downstream - daily data by year - JULY data only
upstream: TNC_23, downstream: TNC_25 (& 24), within former impoundment: 80 & 81; first notch July 2018, completed April 2019
```{r}
coldo %>%
  select(yearf, value = TNC_25, monthf) %>%
  mutate(site = "Downstream") %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_23), yearf, value, monthf), site = "Upstream")) %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_80), yearf, value, monthf), site = "Inside (80)")) %>%
  bind_rows(mutate(select(rename(coldo, value = TNC_81), yearf, value, monthf), site = "Inside (81)")) %>%
  filter(monthf == 7) %>%
  ggplot() +
  geom_boxplot(aes(y = value, x = yearf, fill = site, color = site), 
               alpha = 0.5
              ) +
  theme_bw() +
  scale_fill_manual(values =
                    c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  scale_color_manual(values = c("firebrick","olivedrab",
                      "olivedrab","steelblue")) +
  theme(text = element_text(size = 14)) +
  labs(x = "", y = "Daily mean DO (mg/L) in July",
       title = "Columbia Dam", fill = "", color = "") 


ggsave(here::here("output/Task3_project_impacts/",
                  "PlotZA_columbia_July_DO_up_downstream_by_year.png"),
                  height = 4, width = 6, dpi = 400)
```
# 3.35. Plot ZB: Columbia Dam - monthly mean temperature w/ envelope
TNC_25, 23, 80, 81
Note about adding additional years: you will need to update the numbers in this part: "Montly mean\n2016-17: 0.4 C warmer than upstream\n2019-21: 0.1 C warmer than upstream" which can be found by running the following 2 commands near the bottom of the code chunk:
summary(filter(monthly_diff, yearf %in% 2016:2017)$diff)
summary(filter(monthly_diff, yearf %in% 2019:2050)$diff)
```{r}
# summarize daily temp data by month
tsum_col <-  tdata %>%
    group_by(site, yearf, month, day, dayf) %>%
  summarise(min_temp = min(temp, na.rm = T),
            max_temp = max(temp, na.rm = T),
            mean_temp = mean(temp, na.rm = T),
            .groups = "drop")  %>%
  group_by(site, yearf, month) %>%
  summarize(mean_mean = mean(mean_temp),
            mean_max = mean(max_temp),
            mean_min = mean(min_temp),
            n = length(mean_temp),
            .groups = "drop") %>%
  mutate(mid = case_when(month == 3 ~ yday("2021-03-15"),
                         month == 4 ~ yday("2021-04-15"),
                         month == 5 ~ yday("2021-05-15"),
                         month == 6 ~ yday("2021-06-15"),
                         month == 7 ~ yday("2021-07-15"),
                         month == 8 ~ yday("2021-08-15"),
                         month == 9 ~ yday("2021-09-15"),
                         month == 10 ~ yday("2021-10-15"),
                         month == 11 ~ yday("2021-11-15")
                         )) %>%
  mutate(Month = case_when(month == 4 ~ "April",
                           month == 5 ~ "May",
                           month == 6 ~ "June",
                           month == 7 ~ "July",
                           month == 8 ~ "August",
                           month == 9 ~ "September",
                           month == 10 ~ "October",
                           month == 11 ~ "November",
                           month == 12 ~ "December")) %>%
  filter(site %in% c("TNC_25", "TNC_23", "TNC_80", "TNC_81")) %>%
  mutate(site = case_when(site == "TNC_23" ~ "Upstream",
                          site == "TNC_25" ~ "Downstream",
                          site == "TNC_80" ~ "Inside (80)",
                          site == "TNC_81" ~ "Inside (81)")) %>%
  filter(as.logical(yearf == "2019" & 
                      month == 11 &
                      site == "Upstream") == F)

tsum_envelope <- tdata %>%
  group_by(site, day) %>%
  summarize(multi_min = min(temp),
            multi_max = max(temp),
            .groups = "drop") %>%
  filter(site %in% c("TNC_25", "TNC_23", "TNC_80", "TNC_81")) %>%
  mutate(site = case_when(site == "TNC_23" ~ "Upstream",
                          site == "TNC_25" ~ "Downstream",
                          site == "TNC_80" ~ "Inside (80)",
                          site == "TNC_81" ~ "Inside (81)"))

tsum_col %>%
  ggplot() +
  geom_ribbon(aes(x = day, ymax = multi_max,
                  ymin = multi_min), 
              data = filter(tsum_envelope),
              fill = "gray", alpha = 0.5) +
  geom_line(aes(x = mid, y = mean_mean, color = yearf), size = .5,
             shape = 16,
             position = position_dodge(width = 10)) +      
  geom_point(aes(x = mid, y = mean_mean, color = yearf), size = 2,
             shape = 16,
             position = position_dodge(width = 10)) +
  theme_minimal() +
  labs(x = "", y = "Mean monthly temperature",
       title = "Columbia Dam", color = "") +
  theme(text = element_text(size = 14),
        axis.title.y = element_text(size = 12)) +
    scale_y_continuous(breaks = seq(0,30, by = 10),
                     limits = c(0,32)) +
    scale_x_continuous(
    breaks = c(91, 152, 213, 274, 335),
    limits = c(82, 339),
    labels = c("Apr", "Jun", "Aug",
               "Oct", "Dec")
  ) +
  scale_color_manual(values = c(wes_palettes$Royal1,
                                wes_palettes$Royal2)) +
  facet_wrap(~site) +
  geom_text(aes(x = mid, y = mean_mean, label = mes),
            hjust = 0, size = 2, vjust = 0,
            color = "darkgray",
                       data = data.frame(mid = c(100,100),
                                         mean_mean = c(0.5,0.5),
                          mes = c("Montly mean\n2016-17: 0.4 C warmer than upstream\n2019-21: 0.1 C warmer than upstream", ""),
                                         site = c("Downstream",
                                                  "Upstream")))

monthly_diff <- 
  filter(tsum_col, site == "Downstream") %>%
  left_join(filter(tsum_col, site == "Upstream"),
            by = c("yearf", "month", "mid", "Month")) %>%
  mutate(diff = mean_mean.x - mean_mean.y) %>% 
  filter(n.x >=10,
         n.y >=10)

summary(filter(monthly_diff, yearf %in% 2016:2017)$diff)
summary(filter(monthly_diff, yearf %in% 2019:2050)$diff)

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotZB_columbia_dam_upstream_ds_temp5.png"),
                  height = 4, width = 6.5, dpi = 400)
```
# 3.36. Plot ZC: Columbia downstream (TNC_25) - upstream (TNC_23)
Temp, DO, & Turbidity
```{r}
colall = mutate(col, meas = "Temperature") %>%
  bind_rows(mutate(coldo, meas = "DO")) %>%
  bind_rows(mutate(colturb, meas = "Turbidity"))

colall %>%
  group_by(yearf, meas) %>%
  ggplot() +
  geom_boxplot(aes(x = yearf, y = d25.23), 
               color = "steelblue", 
               fill = "skyblue", alpha = 0.5) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  facet_wrap(~meas, scales = "free") +
  theme_bw() +
  theme(text = element_text(size = 14),
        axis.text.x = element_text(size = 8),
        strip.background = element_rect(fill = "white")) +
  labs(x = "", y = "Difference\n(downstream - upstream)",
       title = "Columbia Dam")

ggsave(here::here("output/Task3_project_impacts/",
                  "PlotZC_columbia_dam_upstream_ds_all.png"),
                  height = 4, width = 6.5, dpi = 400)
```