---
title: "Invertebrates"
author: "Mike Allen"
date: "4/28/2022"
output: html_document
---
# Task 4: Macroinvertebrates and quality scores
a. Visualize and perform statistical analysis of macroinvertebrate and EPA Habitat Assessment scores, including assessing spatial patterns and temporal trends. 

1. Where do sites fall on the optimum/excellent to poor spectrum? 
2. How are scores changing over time at the level of the
individual site and within the broader network as a whole?

b. How are the individual component metrics contributing to the resulting macroinvertebrate and EPA Habitat Assessment scores at the sites? 

For example, are all “Poor” sites classified as such for
the same reason or are there a range of contributing factors?

# Load libraries and read in data
```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(here)
library(lubridate)
library(forcats)
library(GGally)
library(fmsb)
library(wesanderson)

task_path <- "output/Task4_inverts_and_habitat/"

# Read in Macroinvertebrate data
inv16 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2016_2017.xlsx"),
                   skip = 2, 
                   sheet = "macro_2016"
                   ) %>%
  select(c(3,4,32:40)) %>%
  rename(num_gen = 3,
         pct_noninsect = 4,
         pct_ept = 5,
         num_scraper = 6,
         hilsenhoff = 7,
         num_talu2 = 8,
         num_talu3 = 9,
         index = 10,
         rating = 11
         )

inv17 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2016_2017.xlsx"),
                   skip = 3, 
                   sheet = "macro_2017"
                   ) %>%
  select(c(3,4,32:40)) %>%
  rename(tnc_code = 1,
         date = 2,
         num_gen = 3,
         pct_noninsect = 4,
         pct_ept = 5,
         num_scraper = 6,
         hilsenhoff = 7,
         num_talu2 = 8,
         num_talu3 = 9,
         index = 10,
         rating = 11
         )
 
inv18 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2018_2019.xlsx"),
                   skip = 3, 
                   sheet = "macro_2018"
                   ) %>%
  select(c(3,4,32:40)) %>%
  rename(tnc_code = 1,
         date = 2,
         num_gen = 3,
         pct_noninsect = 4,
         pct_ept = 5,
         num_scraper = 6,
         hilsenhoff = 7,
         num_talu2 = 8,
         num_talu3 = 9,
         index = 10,
         rating = 11
         ) %>%
  filter(is.na(tnc_code) == F)

inv19 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2018_2019.xlsx"),
                   skip = 2, 
                   sheet = "macro_2019"
                   ) %>%
  select(c(3,4,32:40)+1) %>%
  rename(num_gen = 3,
         pct_noninsect = 4,
         pct_ept = 5,
         num_scraper = 6,
         hilsenhoff = 7,
         num_talu2 = 8,
         num_talu3 = 9,
         index = 10,
         rating = 11
         )

inv20 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2020_2021.xlsx"),
                   skip = 2, 
                   sheet = "macro_2020"
                   ) %>%
  select(c(3,4,32:40)+1) %>%
  rename(num_gen = 3,
         pct_noninsect = 4,
         pct_ept = 5,
         num_scraper = 6,
         hilsenhoff = 7,
         num_talu2 = 8,
         num_talu3 = 9,
         index = 10,
         rating = 11
         )

inv <- inv16 %>%
  bind_rows(inv17) %>%
  bind_rows(inv18) %>%
  bind_rows(inv19) %>%
  mutate(year = year(date),
         yearf = as.factor(year)) %>%
  mutate(yearf = fct_reorder(yearf, index, .fun = "mean"),
         tnc_code = fct_reorder(tnc_code, index, .fun = "mean"),
         rating = case_when(rating == "EXCELLENT" ~ "Excellent",
                            rating == "GOOD" ~ "Good",
                            rating == "FAIR" ~ "Fair",
                            rating == "POOR" ~ "Poor",
                            TRUE ~ rating))

rm(inv16, inv17, inv18, inv19)

# Read in habitat data
hab16 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2016_2017.xlsx"),
                   skip = 0, 
                   sheet = "Habitat_2016"
                   ) %>%
  select(c(3:17,19:20)) %>%
  rename(epifaunal_sub = 3,
         pool_sub = 4,
         pool_var = 5,
         sed_dep = 6,
         channel_flow = 7,
         channel_alt = 8,
         channel_sin = 9,
         bank_stab_l = 10,
         bank_stab_r = 11,
         bank_veg_l = 12,
         bank_veg_r = 13,
         rip_veg_l = 14,
         rip_veg_r = 15)

# Read in habitat data
hab17 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2016_2017.xlsx"),
                   skip = 0, 
                   sheet = "Habitat_2017"
                   ) %>%
  select(c(3:17,19:20)) %>%
  rename(epifaunal_sub = 3,
         pool_sub = 4,
         pool_var = 5,
         sed_dep = 6,
         channel_flow = 7,
         channel_alt = 8,
         channel_sin = 9,
         bank_stab_l = 10,
         bank_stab_r = 11,
         bank_veg_l = 12,
         bank_veg_r = 13,
         rip_veg_l = 14,
         rip_veg_r = 15)

hab18 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2018_2019.xlsx"),
                   skip = 0, 
                   sheet = "Habitat_2018"
                   ) %>%
  select(c(3:17,19:20)) %>%
  rename(epifaunal_sub = 3,
         pool_sub = 4,
         pool_var = 5,
         sed_dep = 6,
         channel_flow = 7,
         channel_alt = 8,
         channel_sin = 9,
         bank_stab_l = 10,
         bank_stab_r = 11,
         bank_veg_l = 12,
         bank_veg_r = 13,
         rip_veg_l = 14,
         rip_veg_r = 15)

# note: I fixed a typo in Habitat_2019 tab manually:
#         TNC_6	4/12/2019 was TNC_6	4/12/12019
hab19 <- read_xlsx(here("other",
                        "Macro_Habitat_data_dl_20220428",
                        "macro_habitat_data_2018_2019.xlsx"),
                   skip = 0, 
                   sheet = "Habitat_2019"
                   ) %>%
  select(c(3:17,19:20)) %>%
  rename(epifaunal_sub = 3,
         pool_sub = 4,
         pool_var = 5,
         sed_dep = 6,
         channel_flow = 7,
         channel_alt = 8,
         channel_sin = 9,
         bank_stab_l = 10,
         bank_stab_r = 11,
         bank_veg_l = 12,
         bank_veg_r = 13,
         rip_veg_l = 14,
         rip_veg_r = 15)

hab <- hab16 %>%
  bind_rows(hab17) %>%
  bind_rows(hab18) %>%
  bind_rows(hab19) %>%
  rename(date = date_collected) %>%
  mutate(year = year(date),
         yearf = as.factor(year)) %>%
  mutate(yearf = fct_reorder(yearf, habitat_score, .fun = "mean"),
         tnc_code = fct_reorder(tnc_code, habitat_score, 
                                .fun = "mean"),
         rip_veg = rip_veg_r + rip_veg_l,
         bank_veg = bank_veg_r + bank_veg_l,
         bank_stab = bank_stab_r + bank_stab_l) %>%
  select(-c(bank_stab_l, bank_stab_r,
            bank_veg_l, bank_veg_r,
            rip_veg_l, rip_veg_r))

rm(hab16, hab17, hab18, hab19)

```
# Plot A - dot plot of overall index average by site/year
```{r}

inv %>%
  group_by(tnc_code) %>%
  summarize(index_mean = mean(index),
            min = min(index),
            max = max(index),
            n = length(index)) %>%
  mutate(n2 = paste0(c(rep("",20),"n = "), n)) %>%
  ggplot() +
  geom_errorbar(aes(xmin = min, xmax = max, y = tnc_code),
                width = 0, color = "black",
                size = .75) +  
  geom_point(aes(x = index_mean, y = tnc_code),
             size = 3, fill = "skyblue", shape = 21) +

  theme_bw() +
  labs(y = "", x = "Macroinvertebrate Index") +
  geom_text(aes(x = 110, y = tnc_code, label = n2),
            color = "darkgray", hjust = 1)

# ggsave(here(task_path,
#             "PlotA_mean_macroinvertebrate_index_by_site.png"),
#        height = 4, width = 3, dpi = 400)
```
# Macroinvertebrate index table1
values by site & year
```{r}

```

# Macroinvertebrate index table2
mean/sd/min/max/n values by site
```{r}

```
#PlotB - data visualization of index components
Scatterplot matrix to inspect data
```{r}

# ggpairs plot. Found code here:
# https://www.r-bloggers.com/2016/02/multiple-regression-lines-in-ggpairs/
my_smooth_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_point(color = "steelblue", alpha = 0.5, 
               shape = 1, size = 1) + 
    # geom_density_2d(color = "black", size = 0.5, alpha = 0.5) +
    geom_smooth(method=loess, fill="steelblue", color="black", size = 0.5, ...)
  p
}

my_bar_fn <- function(data, mapping, ...){
  the_mean <- mean(data)
  p <- ggplot(data = data, mapping = mapping) + 
    geom_histogram(color = "darkblue", 
                   fill = "steelblue", alpha = 0.5, bins = 15) +
    geom_vline(xintercept = mean(data$x), color = "red")
}

#require(scales)
options(scipen=10000, digits = 0)
g = ggpairs(inv, columns = 3:9, 
            lower = list(continuous = my_smooth_fn),
            diag = list(continuous = my_bar_fn),
            upper = list(continuous = wrap("cor", method = "spearman")),
            columnLabels = c("No. genera",
                             "% non-insects",
                             "% sens. EPT",
                             "No. scrapers",
                             "Hilsenhoff",
                             "No. TALU 2",
                             "No. TALU 3")
            ) +
  theme_bw()
g

# ggsave(plot = g, here(task_path, 
#                "PlotB_macroinvertebrate_scatterplot_matrix.png"), 
#        dpi = 400, width = 7, height = 7)

rm(g)
```
# Plot C - Spiderweb plot of macroinvertebrate index
Code from: https://r-graph-gallery.com/142-basic-radar-chart.html
```{r}
# format data
inv_radar <- inv %>%
  select(c(1, 3:9)) %>%
  group_by(tnc_code) %>%
  summarize_all(mean)


for(i in 1:nrow(inv_radar)){

print(i)

the_title <- as.character(inv_radar$tnc_code[i])

png(here(task_path, 
         "PlotC_macro_radar_plots",
         paste0("PlotC_", the_title, "_macro_radar.png")), res = 400,
    height = 5, width = 5, units = "in")

# data
data <- inv_radar[i,2:8]

# add 2 lines to the dataframe: the max and min you want to show on the plot
data <- rbind(rep(100,7) , rep(0,7) , data)
 
# Make the radarChart !
radarchart( data  , axistype=1 , maxmin = T,
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,100,25),
    cglwd=0.8,
 
    #custom labels
    vlcex=0.8, title = the_title
    )
dev.off()
}
```
# Plot D - macroinvertebrate index over time (separate plots by site)
```{r}
# for testing
i <- unique(inv$tnc_code)[13]
for(i in unique(inv$tnc_code)){

print(i)

color_vector <- c("olivedrab",
            "olivedrab2",
            wes_palettes$BottleRocket2[1:2])

plot_data <- inv %>%
  mutate(rating = fct_reorder(rating, index, .desc = T)) %>%
  filter(tnc_code == i) 

plot_data %>%
  group_by(year) %>%
  summarize(index = mean(index)) %>%
  ggplot() +
  geom_hline(yintercept = 63, lty = 2, color = color_vector[1],
             alpha = 0.75) +
  geom_hline(yintercept = 42, lty = 2, color = color_vector[2],
             alpha = 0.75) +
  geom_hline(yintercept = 21, lty = 2, color = color_vector[3],
             alpha = 0.75) +
  geom_hline(yintercept = 0, lty = 2, color = color_vector[4],
             alpha = 0.75) +
  geom_line(aes(x = year, y = index), 
            color = "darkgray",
            size = 1) +
  geom_point(aes(x = year, y = index, color = rating), 
            size = 4, data = plot_data) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_x_continuous(breaks = 2016:2021) +
  scale_color_manual(values = color_vector,
                     drop = F) +
    theme_classic() +
    theme(text = element_text(size = 14)) +
    labs(y = "Macroinvertebrate Index", x = "",
         color = "Rating",
         title = i)

ggsave(here(task_path, "PlotD_macro_by_year",
              paste0("PlotD_macro_by_year_site_", i, ".png")),
         width = 6, height = 4, dpi = 400)
}

```
# Plot E - macroinvertebrate index over time at Columbia Dam sites
```{r}
sites <- c("TNC_25", "TNC_23", "TNC_80")
inv %>%
  filter(tnc_code %in% sites) %>%
  group_by(tnc_code, year) %>%
  summarize(index = mean(index)) %>%
  ggplot() +
  geom_line(aes(x = year, y = index, color = tnc_code), 
            size = 1) +
  geom_point(aes(x = year, y = index, color = tnc_code), 
            size = 4) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_color_manual(values = c("olivedrab", "orange")) +
    theme_bw() +
    theme(text = element_text(size = 14)) +
    labs(y = "Macroinvertebrate Index", x = "",
         title = "Columbia Dam", color = "")

  ggsave(here(task_path, 
              "PlotE_macro_by_year_Columbia_Dam.png"),
         width = 6, height = 4, dpi = 400)

```
# Plot F - macroinvertebrate index over time at Paulina Dam sites
```{r}
sites <- c("TNC_18", "TNC_19")
inv %>%
  filter(tnc_code %in% sites) %>%
  group_by(tnc_code, year) %>%
  summarize(index = mean(index)) %>%
  ggplot() +
  geom_line(aes(x = year, y = index, color = tnc_code), 
            size = 1) +
  geom_point(aes(x = year, y = index, color = tnc_code), 
            size = 4) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_color_manual(values = c("olivedrab", "orange")) +
    theme_bw() +
    theme(text = element_text(size = 14)) +
    labs(y = "Macroinvertebrate Index", x = "",
         title = "Paulina Dam", color = "")

  ggsave(here(task_path, 
              "PlotE_macro_by_year_Paulina_Dam.png"),
         width = 6, height = 4, dpi = 400)

```
# Plot G - dot plot of overall index average habitat score by site/year
```{r}

hab %>%
  group_by(tnc_code) %>%
  summarize(index_mean = mean(habitat_score),
            min = min(habitat_score),
            max = max(habitat_score),
            n = length(habitat_score)) %>%
  mutate(n2 = paste0(c(rep("",20),"n = "), n)) %>%
  ggplot() +
  geom_errorbar(aes(xmin = min, xmax = max, y = tnc_code),
                width = 0, color = "black",
                size = .75) +  
  geom_point(aes(x = index_mean, y = tnc_code),
             size = 3, fill = wes_palettes$BottleRocket2[1], 
             shape = 21) +
  theme_bw() +
  labs(y = "", x = "Habitat Score") +
  geom_text(aes(x = 245, y = tnc_code, label = n2),
            color = "darkgray", hjust = 1)

ggsave(here(task_path,
            "PlotG_mean_habitat_score_by_site.png"),
       height = 4, width = 3, dpi = 400)
```
# Plot H - macroinvertebrate index vs. habitat score
```{r}
hab %>%
  left_join(inv, by = c("tnc_code", "year", "yearf")) %>%
  group_by(tnc_code) %>%
  summarize(index_mean = mean(index, na.rm = T),
            index_min = min(index, na.rm = T),
            index_max = max(index, na.rm = T),
            index_n = sum(is.na(index)==F),
            hab_mean = mean(habitat_score, na.rm = T),
            hab_min = min(habitat_score, na.rm = T),
            hab_max = max(habitat_score, na.rm = T),
            hab_n = sum(is.na(habitat_score)==F)) %>%
  mutate(index_n2 = paste0(c(rep("",20),"n = "), index_n),
         hab_n2 = paste0(c(rep("",20),"n = "), hab_n),
         num = gsub(tnc_code, pattern = "TNC_", 
                    replacement = "")) %>%
  ggplot() +
  geom_errorbar(aes(xmin = hab_min, xmax = hab_max, y = index_mean),
                width = 0, color = "darkgray",
                size = .75, alpha = .5) +  
  geom_errorbar(aes(ymin = index_min, 
                    ymax = index_max, x = hab_mean),
                width = 0, color = "darkgray",
                size = .75, alpha = .5) +  
  geom_point(aes(y = index_mean, x = hab_mean),
             size = 5, fill = "olivedrab2", 
             shape = 21) +
  theme_bw() +
  labs(x = "Habitat Score",
       y = "Macroinvertebrate Index") +
  geom_text(aes(y = index_mean, x = hab_mean, label = num),
            color = "black", hjust = .5, size = 2.5)

ggsave(here(task_path,
            "PlotH_habitat_score_vs_macro_by_site.png"),
       height = 4, width = 6, dpi = 400)

```
#Plot I - data visualization of habitat score components
Scatterplot matrix to inspect data
1. Epifaunal Substrate/Available Cover	2. Pool Substrate Characterization	3. Pool variability	4. Sediment Deposition	5. Channel Flow Status	6. Channel Alteration	7. Channel sinuosity	8. Bank Stability-LB	8. Bank Stability-RB	9. Bank vegetation Protection-LB	9. Bank vegetation Protection-RB	10. Ripariarn Vegetation Zone Width-LB	10. Ripariarn Vegetation Zone Width-RB

```{r}

# ggpairs plot. Found code here:
# https://www.r-bloggers.com/2016/02/multiple-regression-lines-in-ggpairs/
my_smooth_fn <- function(data, mapping, ...){
  p <- ggplot(data = data, mapping = mapping) + 
    geom_point(color = "steelblue", alpha = 0.5, 
               shape = 1, size = 1) + 
    # geom_density_2d(color = "black", size = 0.5, alpha = 0.5) +
    geom_smooth(method=loess, fill="steelblue", color="black", size = 0.5, ...)
  p
}

my_bar_fn <- function(data, mapping, ...){
  the_mean <- mean(data)
  p <- ggplot(data = data, mapping = mapping) + 
    geom_histogram(color = "darkblue", 
                   fill = "steelblue", alpha = 0.5, bins = 15) +
    geom_vline(xintercept = mean(data$x), color = "red")
}

#require(scales)
options(scipen=10000, digits = 0)
g = ggpairs(hab, columns = 3:16, 
            lower = list(continuous = my_smooth_fn),
            diag = list(continuous = my_bar_fn),
            upper = list(continuous = wrap("cor", method = "spearman")),
            columnLabels = c("Epifaun. sub.",
                             "Pool sub.",
                             "Pool var.",
                             "Sediment dep.",
                             "Channel flow",
                             "Channel alt.",
                             "Channel sin.",
                             "Bank stab. L",
                             "Bank stab. R",
                             "Bank veg. L",
                             "Bank veg. R",
                             "Rip. zone L",
                             "Rip. zone R",
                             "Habitat score")
            ) +
  theme_bw() +
  theme(strip.text = element_text(size = 6))
g

ggsave(plot = g, here(task_path,
               "PlotI_macroinvertebrate_scatterplot_matrix.png"),
       dpi = 400, width = 10, height = 10)

rm(g)
```
# Plot J - Spiderweb plot of habitat score data
Code from: https://r-graph-gallery.com/142-basic-radar-chart.html
```{r}
# format data
hab_radar <- hab %>%
  select(c(1, 3:9, 14:16)) %>%
  group_by(tnc_code) %>%
  summarize_all(mean)


for(i in 1:nrow(hab_radar)){

print(i)

the_title <- as.character(hab_radar$tnc_code[i])

png(here(task_path, 
         "PlotJ_habitat_radar_plots",
         paste0("PlotJ_", the_title, "_habitat_radar.png")), 
    res = 400,
    height = 5, width = 5, units = "in")

# data
data <- hab_radar[i,2:11]

# add 2 lines to the dataframe: the max/min you want to show on plot
data <- rbind(rep(20,10) , rep(0,10) , data)
 
# Make the radarChart !
radarchart( data  , axistype=1 , maxmin = T,
 
    #custom polygon
    pcol=rgb(0.2,0.5,0.5,0.9) , pfcol=rgb(0.2,0.5,0.5,0.5) , plwd=4 , 
 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(0,20,5),
    cglwd=0.8,
 
    #custom labels
    vlcex=0.8, title = the_title
    )
dev.off()
}
```

# Plot K - habitat score over time (separate plots by site)
```{r}
# for testing 
i = unique(hab$tnc_code)[1]

for(i in unique(hab$tnc_code)){

print(i)

color_vector <- c("olivedrab",
            wes_palettes$BottleRocket2[1:2])

plot_data <- hab %>%
  mutate(habitat_rating = fct_reorder(habitat_rating, habitat_score, 
                              .desc = T)) %>%
  filter(tnc_code == i) 

hab %>%
  filter(tnc_code == i) %>%
  group_by(year, habitat_rating) %>%
  summarize(habitat_score = mean(habitat_score, na.rm = T),
            .groups = "drop") %>%
  ggplot() +
  geom_hline(yintercept = 155, lty = 2, color = color_vector[1],
             alpha = 0.75) +
  geom_hline(yintercept = 105, lty = 2, color = color_vector[2],
             alpha = 0.75) +
  geom_hline(yintercept = 55, lty = 2, color = color_vector[3],
             alpha = 0.75) +
  geom_line(aes(x = year, y = habitat_score), 
            color = "darkgray",
            size = 1) +
  geom_point(aes(x = year, y = habitat_score, 
                 color = habitat_rating), 
            size = 4, data = plot_data) +
  scale_y_continuous(limits = c(0, 200)) +
  scale_color_manual(values = color_vector,
                     drop = F) +
    theme_classic() +
    theme(text = element_text(size = 14)) +
    labs(y = "Habitat Score", x = "",
         color = "Rating",
         title = i)

  ggsave(here(task_path, "PlotK_habitat_score_by_year",
              paste0("PlotK_hab_score_by_year_site_", i, ".png")),
         width = 6, height = 4, dpi = 400)
}

```
# Plot L - macroinvertebrate index over time (separate plots by site)
```{r}
# for testing
i <- unique(inv$tnc_code)[13]
for(i in unique(inv$tnc_code)){

print(i)

color_vector_inv <- c("olivedrab",
            "olivedrab2",
            wes_palettes$BottleRocket2[1:2])

color_vector_hab <- c("olivedrab",
            wes_palettes$BottleRocket2[1:2])

plot_data_inv <- inv %>%
  mutate(rating = fct_reorder(rating, index, .desc = T)) %>%
  filter(tnc_code == i) 

line_data_inv <- plot_data_inv %>%
  group_by(year) %>%
  summarize(index = mean(index)) 

plot_data_hab <- hab %>%
  mutate(habitat_rating = fct_reorder(habitat_rating, habitat_score, 
                              .desc = T)) %>%
  filter(tnc_code == i) 

line_data_hab <- plot_data_hab %>%
  filter(tnc_code == i) %>%
  group_by(year, habitat_rating) %>%
  summarize(habitat_score = mean(habitat_score, na.rm = T),
            .groups = "drop")

  ggplot() +
  geom_line(aes(x = year, y = index), 
            color = "darkgray",
            size = 1,
            data = line_data_inv) +
  geom_point(aes(x = year, y = index, color = rating), 
            size = 4, data = plot_data_inv) +
  geom_line(aes(x = year, y = habitat_score/2),
            color = "darkgray",
            size = 1,
            data = line_data_hab) +
  geom_point(aes(x = year, y = habitat_score/2,
                 color = habitat_rating),
            size = 4, data = plot_data_hab) +
  scale_y_continuous(limits = c(0, 100)) +
  scale_x_continuous(breaks = 2016:2021) +
  scale_color_manual(values = color_vector,
                     drop = F) +
    theme_classic() +
    theme(text = element_text(size = 14)) +
    labs(y = "Macroinvertebrate Index", x = "",
         color = "Invertebrate",
         title = i)

ggsave(here(task_path, "PlotD_macro_by_year",
              paste0("PlotD_macro_by_year_site_", i, ".png")),
         width = 6, height = 4, dpi = 400)
}
```